\newpage
\begin{thebibliography}{99}

\bibitem{AZ90}
Artis, M. J., \& Zhang, W. (1990). BVAR forecasts for the G-7. International journal of forecasting, 6(3), 349-362.

\bibitem{Theta00}
Assimakopoulos, V., \& Nikolopoulos, K. (2000). The theta model: a decomposition approach to forecasting. International journal of forecasting, 16(4), 521-530. 

\bibitem{Bates69}
Bates, J. M., \& Granger, C. W. (1969). The combination of forecasts. Journal of the Operational Research Society, 20(4), 451-468.

\bibitem{BKZ11}
Beauchemin, K. R., \& Zaman, S. (2011). A medium scale forecasting model for monetary policy.

\bibitem{BOH13}
Berg, T. O., \& Henzel, S. (2013). Point and Density Forecasts for the Euro Area Using Many Predictors: Are Large BVARs Really Superior? (No. 155). ifo Working Paper.

\bibitem{BJ70}
Box, G. E. P., \& Jenkins, G. M. (1970). Time series analysis: forecasting and control, 1976. ISBN: 0-8162-1104-3.y.

\bibitem{Brown59}
Brown, R. G. (1959). Statistical forecasting for inventory control. McGraw/Hill.

\bibitem{CKM12}
Carriero, A., Kapetanios, G., \& Marcellino, M. (2012). Forecasting government bond yields with large Bayesian vector autoregressions. Journal of Banking \& Finance, 36(7), 2026-2047.

\bibitem{CK94}
Carter, C. K., \& Kohn, R. (1994). On Gibbs sampling for state space models. Biometrika, 541-553.

\bibitem{CS05}
Cogley, T., \& Sargent, T. J. (2005). Drifts and volatilities: monetary policies and outcomes in the post WWII US. Review of Economic dynamics, 8(2), 262-302.

\bibitem{NP15}
Del Negro, M., \& Primiceri, G. E. (2015). Time varying structural vector autoregressions and monetary policy: a corrigendum. The review of economic studies, 82(4), 1342-1345.

\bibitem{DM15}
Demeshev, B., \& Malakhovskaya, O. (2015). Forecasting Russian macroeconomic indicators with BVAR.

\bibitem{DGT94}
Deutsch, M., Granger, C. W., \& Teräsvirta, T. (1994). The combination of forecasts using changing weights. International Journal of Forecasting, 10(1), 47-57.

\bibitem{DLS84}
Doan, T., Litterman, R., \& Sims, C. (1984). Forecasting and conditional projection using realistic prior distributions. Econometric reviews, 3(1), 1-100.

\bibitem{Fuke90}
Funke, M. (1990). Assessing the forecasting accuracy of monthly vector autoregressive models: The case of five OECD countries. International Journal of Forecasting, 6(3), 363-378.

\bibitem{GR84}
Granger, C. W., \& Ramanathan, R. (1984). Improved methods of combining forecasts. Journal of forecasting, 3(2), 197-204.

\bibitem{Holt57}
Holt, C. C. (1957). Forecasting seasonals and trends by exponentially weighted moving averages, ONR Memorandum (Vol. 52), Pittsburgh, PA: Carnegie Institute of Technology. Available from the Engineering Library, University of Texas at Austin.

\bibitem{HB08}
Hyndman, R. J., \& Billah, B. (2003). Unmasking the Theta method. International Journal of Forecasting, 19(2), 287-290.

\bibitem{Hyndman08}
Hyndman, R. J., \& Khandakar, Y. (2007). Automatic time series for forecasting: the forecast package for R (No. 6/07). Monash University, Department of Econometrics and Business Statistics.

\bibitem{HKSG02}
Hyndman, R. J., Koehler, A. B., Snyder, R. D., and Grose, S. A state space framework for automatic forecasting using exponential smoothing methods // 2002 International Journal of Forecasting, 18, 439 - 454.

\bibitem{KSC98}
Kim, S., Shephard, N., \& Chib, S. (1998). Stochastic volatility: likelihood inference and comparison with ARCH models. The review of economic studies, 65(3), 361-393.

\bibitem{KK09}
Koop, G., \& Korobilis, D. (2010). Bayesian multivariate time series methods for empirical macroeconomics. Foundations and Trends® in Econometrics, 3(4), 267-358.

\bibitem{KPSS92}
Kwiatkowski, D., Phillips, P. C., Schmidt, P., \& Shin, Y. (1992). Testing the null hypothesis of stationarity against the alternative of a unit root: How sure are we that economic time series have a unit root?. Journal of econometrics, 54(1-3), 159-178.

\bibitem{Litterman86}
Litterman, R. (1986). Forecasting with Bayesian vector autoregressions—Five years of experience: Robert B. Litterman, Journal of Business and Economic Statistics 4 (1986) 25–38. International Journal of Forecasting, 2(4), 497-498.

\bibitem{Muth60}
Muth, J. F. (1960). Optimal properties of exponentially weighted forecasts. Journal of the american statistical association, 55(290), 299-306.

\bibitem{OSCB}
Osborn, D. R. (1988). Seasonality and habit persistence in a life cycle model of consumption. Journal of Applied Econometrics, 3(4), 255-266.

\bibitem{Primiceri05}
Primiceri, G. E. (2005). Time varying structural vector autoregressions and monetary policy. The Review of Economic Studies, 72(3), 821-852.

\bibitem{Sims80}
Sims, C. A. (1980). Macroeconomics and reality. Econometrica: Journal of the Econometric Society, 1-48.

\bibitem{Winters60}
Winters, P. R. (1960). Forecasting sales by exponentially weighted moving averages. Management science, 6(3), 324-342.

\bibitem{Yule27}
Yule, G. U. (1927). On a method of investigating periodicities in disturbed series, with special reference to Wolfer's sunspot numbers. Philosophical Transactions of the Royal Society of London. Series A, Containing Papers of a Mathematical or Physical Character, 226, 267-298.


\end{thebibliography}
